Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-09-14 Grassmannian_cells.tex
Streamlining presentation of truncated preprojective representations

\newtheorem{theorem}{Theorem}[section]
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\ui}{\underline i}
\newcommand{\uj}{\underline j}
\newcommand\udim{{\underline{\dim}\, }}

\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\setcounter{MaxMatrixCols}{20}
\title{Cell Decomposition of Rank 2 Quiver Grassmannians}

@@

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations.%, but the vertices $1$ and $2$ are exchanged. 
%Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
\begin{theorem}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_1 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
\end{remark}

\begin{lemma}
  For any $m\ge1$, we have 
  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
\end{lemma}
\begin{proof} 
  Note that we have an Auslander-Reiten sequence
  \begin{equation}
    \label{eq:AR sequence}
    0\longrightarrow P_{m-1}\stackrel{\iota}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
  \end{equation}
  with irreducible homomorphisms $f_i$ which are also linearly independent. 
  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
\end{proof}

Write $P_{m+1}^{\{f_1,\ldots,f_k\}}$ for the cokernel of the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$, i.e. we have a short exact sequence
\begin{equation}
\label{eq:truncated preprojectives}
  0\longrightarrow P_m^k\stackrel{[f_1\ \cdots\ f_k]}{\longrightarrow} P_{m+1}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.
\end{equation}

\begin{lemma}
  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the following hold:
  \begin{enumerate}
    \item $\Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})$ is naturally isomorphic to $\Hom(P_m,P_{m+1})/\kk f_1\oplus\cdots\oplus\kk f_k$;
    \item $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ is naturally isomorphic to $\kk f_1\oplus\cdots\oplus\kk f_k$;
    \item $\Hom(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)=0$.
  \end{enumerate}
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives the exact sequence
  \[0\longrightarrow \Hom(P_m,P_m^k)\stackrel{[f_1\ \cdots\ f_k]\circ}{\longrightarrow} \Hom(P_m,P_{m+1})\longrightarrow \Hom(P_m,P_{m+1}^{\{f_1,\ldots,f_k\}})\longrightarrow 0,\]
  establishing (1).

  To see (2), we apply the functor $\Hom(-,P_m)$ to the sequence \eqref{eq:truncated preprojectives} to get an isomorphism $\Hom(P_m^k,P_m)\cong\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$.
  Observe that $\Hom(P_m^k,P_m)$ is spanned by the coordinate projections $\pi_i:P_m^k\to P_m$ for $1\le i\le k$ and each of these gives rise to a commutative diagram
  \[\xymatrix{ & 0\ar[d] & 0\ar[d] & & \\ & P_m^{k-1}\ar[d]\ar@{=}[r]& P_m^{k-1}\ar[d]^{[f_1\ \cdots\ \widehat{f_i}\ \cdots\ f_k]}& & \\
    0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d]^{\pi_i}\ar@{}[dr]|(.35){\ulcorner}& P_{m+1}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar@{=}[d]& 0 \\
    0\ar[r]& P_m\ar[r]^(.35){f_i}\ar[d]& P_{m+1}^{\{f_1,\ldots,\widehat{f_i},\ldots,f_k\}}\ar[r]\ar[d]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0\\
     & 0 & 0 & & }\]
  where $\hat f_i$ above indicates that the function $f_i$ has been omitted.
  The bottom row of this diagram is the extension from $\Ext(P_{m+1}^{\{f_1,\ldots,f_k\}},P_m)$ which is naturally identified with the generator $f_i$ of $\kk f_1\oplus\cdots\oplus\kk f_k$.

  Part (3) follows immediately from $\Hom(P_{m+1},P_m)=0$.
	%(2) and the observation that 
  %\[\langle P_{m+1}^{\{f_1,\ldots,f_k\}},P_m\rangle=\langle P_{m+1},P_m\rangle-k\langle P_m,P_m\rangle=-k.\]
\end{proof}

\begin{lemma}
  Let $f_1,\ldots,f_n\in\Hom(P_m,P_{m+1})$ be linearly independent morphisms and write $g:P_{m-1}\to P_m$ for the composition of the inclusion $\iota:P_{m-1}\hookrightarrow P_m^n$ from \eqref{eq:AR sequence} with the projection $\pi_n:P_m^n\to P_m$ to the $n$-th factor.  Then $P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}=P_m^{\{g\}}$.
\end{lemma}
\begin{proof}
  We have the following commutative diagram
  \[\xymatrix{0\ar[r]& P_m^{n-1}\ar@{=}[d]\ar[r]& P_m^n\ar[r]^{\pi_n}\ar[d]^{[f_1\ \cdots\ f_n]}\ar@{}[dr]|(.65){\lrcorner}& P_m\ar[r]\ar[d]^{f_n}& 0 \\
  0\ar[r]& P_m^{n-1}\ \ \ \ar[r]^{[f_1\ \cdots\ f_{n-1}]}&\ \ \ P_{m+1}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}\ar[r]& 0}\]
  Since the vertical morphism on the left is an equality, the right hand square is a pullback.  
  But this implies the kernels of the vertical morphisms coincide.

  The middle vertical morphism fits into the exact sequence \eqref{eq:AR sequence} and so its kernel is $P_{m-1}$.
  It follows that the resulting morphism $g:P_{m-1}\to P_m$, which is the kernel of the right-hand vertical morphism, satisfies $P_m^{\{g\}}=P_{m+1}^{\{f_1,\ldots,f_{n-1}\}}$.
\end{proof}

For any nonempty subset $I\subset[1,k]$, say with $|I|=\ell$, we get an exact sequence
\[0\longrightarrow P_m^\ell\stackrel{[f_i]_{i\in I}}{\longrightarrow} P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\longrightarrow P_{m+1}^{\{f_1,\ldots,f_k\}}\longrightarrow 0.\]
Each such sequence has the following almost-split property for subrepresentations of $P_{m+1}^{\{f_1,\ldots,f_k\}}$.
\begin{lemma}
  For $m\ge1$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, given any proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$, the upper pullback sequence
  \[\xymatrix{0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r] & V^I\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}} & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]& P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]& 0}\]
  splits for every $I\subset[1,k]$.
\end{lemma}
\begin{proof}
  When $I=\varnothing$, we have $\ell=0$ and there is nothing to show, so assume $I$ is a nontrivial subset of $[1,k]$.

  We proceed by simultaneous induction on $k$ and $\ell=|I|$.  For any nonzero $f\in\Hom(P_m,P_{m+1})$ the exact sequence
  \[\xymatrix{0\ar[r] & P_m\ar[r]^f & P_{m+1}\ar[r] & P_{m+1}^{\{f\}}\ar[r] & 0}\]
  is almost split, giving the claim in the case $k=\ell=1$.  For $k>1$ and a nontrivial proper subset $I\subsetneq[1,k]$, we have the following commutative diagram
  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_i\}_{i\in I}}\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & P_{m+1}^{\{f_j\}_{j\in[1,k]\setminus I}}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ gives rise, via pullbacks, to the following commutative diagram
  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_m^{k-\ell}\ar@{=}[r]\ar[d]^{[f_j]_{j\in[1,k]\setminus I}} & P_m^{k-\ell}\ar[d]^{[f_j]_{j\in[1,k]\setminus I}}\ar[r] & 0 \\
  0\ar[r] & P_m^\ell\ar@{=}[d]\ar[r]^{[f_i]_{i\in I}} & V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^\ell\ar[r]^(.35){[f_i]_{i\in I}}\ar[d] & V^I\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
  in which the middle vertical sequence and the middle horizontal sequence split by induction.  
  But the images of $[f_i]_{i\in I}$ and $[f_j]_{j\in[1,k]\setminus I}$ intersect trivially inside $V^{[1,k]}$ and thus the lower horizontal sequence must split as well, establishing the claim for $I\subsetneq[1,k]$.

  For $I=[1,k]$, we consider the commutative diagram
  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & P_{m+1}\ar@{=}[r]\ar[d] & P_{m+1}\ar[d]\ar[r] & 0 \\
  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & P_{m+1}\oplus P_{m+1}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & P_{m+1}^{\{f_1\ \cdots\ f_{k-1}\}}\oplus P_{m+1}^{\{f_k\}}\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^k\ar[r]^{[f_1\ \cdots\ f_k]}\ar[d] & P_{m+1}\ar[r]\ar[d] & P_{m+1}^{\{f_1,\ldots,f_k\}}\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
  A proper subrepresentation $V\subsetneq P_{m+1}^{\{f_1,\ldots,f_k\}}$ then gives rise to the following commutative diagram
  \[\xymatrix{ & & 0\ar[d] & 0\ar[d] & \\   & 0\ar[r]\ar[d] & V^{[1,k]}\ar@{=}[r]\ar[d]^{\Delta} & V^{[1,k]}\ar[d]\ar[r] & 0 \\
  0\ar[r] & P_m^{k-1}\oplus P_m\ar@{=}[d]\ar[r] & V^{[1,k]}\oplus V^{[1,k]}\ar[r]\ar[d]\ar@{}[dr]|{\lrcorner} & V^{[1,k]\setminus I}\oplus V^I\ar[d]\ar[r] & 0 \\
  0\ar[r]& P_m^k\ar[r]\ar[d] & V^{[1,k]}\ar[r]\ar[d] & V\ar[r]\ar[d]& 0\\ & 0 & 0 & 0 & }\]
  in which the middle vertical sequence splits and the middle horizontal sequence is split by induction.  
  But the image of $[f_1\ \cdots\ f_k]:P_m^{k-1}\oplus P_m\to V^{[1,k]}\oplus V^{[1,k]}$ and the diagonal $\Delta:V^{[1,k]}\to V^{[1,k]}\oplus V^{[1,k]}$ intersect trivially because $f_1,\ldots,f_k$ are linearly independent.
  As above the lower horizontal sequence also splits, establishing the claim for $I=[1,k]$.
\end{proof}

>>>>

\newtheorem{theorem}{Theorem}[section]
\newtheorem{claim}[theorem]{Claim}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{question}[theorem]{Question}
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{remark}[theorem]{Remark}

\newcommand{\bfe}{\mathbf{e}}
\newcommand{\bff}{\mathbf{f}}
\newcommand{\bfg}{\mathbf{g}}
\newcommand{\bfi}{\mathbf{i}}
\newcommand{\bfh}{\mathbf{h}}
\newcommand{\tbfe}{{\tilde\bfe}}
\newcommand{\tbff}{{\tilde\bff}}
\newcommand{\tbfg}{{\tilde\bfg}}
\newcommand{\tbfh}{{\tilde\bfh}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\cC}{\mathcal{C}}
\newcommand{\cP}{\mathcal{P}}
\newcommand{\ui}{\underline i}
\newcommand{\uj}{\underline j}
\newcommand\udim{{\underline{\dim}\, }}

\newcommand{\Rep}{\mathrm{Rep}}
\newcommand{\rep}{\operatorname{rep}}
\newcommand{\Gr}{\mathrm{Gr}}
\renewcommand{\AA}{\mathbb{A}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\kk}{\Bbbk}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\im}{\operatorname{im}}
\newcommand{\codim}{\operatorname{codim}}
\newcommand{\into}{\hookrightarrow}
\newcommand{\onto}{\to\!\!\!\!\!\to}
\newcommand{\ses}[3]{0\rightarrow #1\rightarrow #2\rightarrow#3\rightarrow 0}
\newcommand{\Sc}[2]{\langle #1,#2\rangle}
\newcommand{\spn}{\operatorname{span}}
\setcounter{MaxMatrixCols}{20}
\title{Cell Decomposition of Rank 2 Quiver Grassmannians}

@@

\noindent Denote by $K(n)$ the \emph{$n$-Kronecker quiver} $1\stackrel{n}{\longleftarrow}2$ with vertices $K_0(n)=\{1,2\}$ and $n$ arrows from vertex $2$ to vertex $1$. 
Write $\Sigma_1$ and $\Sigma_2$ for the BGP-reflection functors of $K(n)$ \cite{bgp}. 
Note that (up to relabeling vertices) the quiver $K(n)$ itself does not change when applying the reflection functors and thus we view them as endofunctors acting on the category $\rep K(n)$ of finite-dimensional representations. %, but the vertices $1$ and $2$ are exchanged. 
With this identification of $K(n)$ and $K(n)^{op}$, the endofunctors $\Sigma_1\Sigma_2$ and $\Sigma_2\Sigma_1$ are each naturally isomorphic to the identity.
%Let $$\Sigma:=\begin{cases}\Sigma_1\text{ if vertex }1 \text{ is a source;}\\\Sigma_2\text{ if vertex }$2$ \text{ is a source.}\end{cases}$$

Define Chebyshev polynomials $u_k$ for $k\in\ZZ$ by the recursion $u_0=0$, $u_1=1$, $u_{k+1}=nu_k-u_{k-1}$.
\begin{theorem}
  For each $m\ge1$, there exist unique (up to isomorphism) indecomposable rigid representations $P_m$ and $I_m$ of $K(n)$ with dimension vectors $(u_m,u_{m-1})$ and $(u_{m-1},u_m)$ respectively. 
  Moreover, any rigid representation of $K(n)$ is isomorphic to one of the form $P_m^{a_1}\oplus P_{m+1}^{a_2}$ or $I_m^{a_1}\oplus I_{m+1}^{a_2}$ for some $m\ge1$ and some $a_1,a_2\ge0$.
\end{theorem}
The representations $P_m$ are called the \emph{preprojective} representations of $K(n)$ and the representations $I_m$ are called \emph{preinjective}.
\begin{remark}
  These representations satisfy the following recursions using the reflection functors:
  \[P_1=S_1,\quad P_m=\Sigma_2 P_{m-1},\quad I_1=S_2,\quad I_m=\Sigma_1 I_{m-1}\]
  for $m\ge2$.
\end{remark}

Write $H_m:=\Hom(P_m,P_{m+1})$ for $m\ge1$.  
For each $m\ge2$, there is an Auslander-Reiten sequence \cite{auslander-reiten-smalo}
\begin{equation}
  \label{eq:AR sequence}
  0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m\otimes H_m\stackrel{ev}{\longrightarrow} P_{m+1}\longrightarrow 0,
\end{equation}
where the right-hand morphism is the natural evaluation map.

Write $Gr(H_m)$ for the \emph{total Grassmannian} of $H_m$ whose elements are nontrivial proper subspaces $V\subset H_m$.
Some results below remain true if we allow $H_m$ or $0$ as elements of $Gr(H_m)$, but not all, so for uniformity of exposition we omit these possibilities.
\begin{lemma}
  \label{le:injective evaluation maps}
  For any $V\in Gr(H_m)$, the natural evaluation map $ev_V:P_m\otimes V\to P_{m+1}$ is injective.
\end{lemma}

%%%%%%%%%%%%%%%%%%%
% needs polishing %
%%%%%%%%%%%%%%%%%%%
%\begin{proof}
%  A nonzero element $f\in V$ corresponds to an irreducible morphism $f:P_m\to P_{m+1}$ and thus does not factor through any representation $Z\ne P_m$, in particular $f$ is injective.
%  But any nonzero element of $\ker ev_V$ gives rise to a nonzero $f\in V$ which is not injective and thus $ev_V$ must be an injective map.
%\end{proof}

%\begin{lemma}
%  For any $m\ge1$, we have 
%  \[\dim\Hom(P_m,P_m)=1,\quad \dim\Hom(P_m,P_{m+1})=n,\quad \dim\Hom(P_{m+1},P_m)=0, \quad\dim\Ext(P_{m+1},P_m)=0.\]  
%  Moreover, for $1\le k<n$ and linearly independent functions $f_1,\ldots,f_k\in\Hom(P_m,P_{m+1})$, the map $[f_1\ \cdots\ f_k]:P_m^k\to P_{m+1}$ is injective. 
%\end{lemma}
%\begin{proof} 
%  Note that we have an Auslander-Reiten sequence
%  \begin{equation}
%    \label{eq:AR sequence}
%    0\longrightarrow P_{m-1}\stackrel{\iota_{m-1}}{\longrightarrow} P_m^n\stackrel{[f_1\ \cdots\ f_n]}{\longrightarrow} P_{m+1}\longrightarrow 0
%  \end{equation}
%  with irreducible homomorphisms $f_i$ which are also linearly independent. 
%  Thus they do not factor through a representation $Z\neq P_{m}$ which already means that they are injective, see for instance \cite[Lemma 1.6]{ass}. 
%  If we pick $k<n$ linearly independent homomorphisms $f_{i_1},\ldots, f_{i_k}$, this also means that $[f_{i_1}\ \cdots\ f_{i_k}]:P_m^k\to P_{m+1}$ is injective. 
%  Indeed otherwise, at least one of the homomorphisms would be forced to factor through a representation $Z\neq P_{m}$.
%\end{proof}
%\begin{remark}
%  Fix a basis $\{f_{m,1},\ldots,f_{m,n}\}$ for $\Hom(P_m,P_{m+1})$, $m\ge2$.
%  Define a basis $\{f_{\ell,1},\ldots,f_{\ell,n}\}$ for each $\Hom(P_\ell,P_{\ell+1})$, $1\le\ell\le m-1$, by downward induction as follows.  
%  Write $\iota_\ell:P_\ell\to P_{\ell+1}^n$ for the left-hand morphism from the sequence \eqref{eq:AR sequence} computed using $f_k=f_{\ell+1,k}$, $1\le k\le n$. 
%  Then the basis element $f_{\ell,k}$ is given by composing $\iota_\ell$ with the coordinate projection $\pi_k:P_{\ell+1}^n\to P_{\ell+1}$ onto the $k$-th factor.
%  Indeed, applying $\Hom(-,P_{\ell+1})$ to this sequence \eqref{eq:AR sequence} gives an isomorphism $\Hom(P_{\ell+1}^n,P_{\ell+1})\cong\Hom(P_\ell,P_{\ell+1})$ whereby the natural basis of coordinate projections on the left is taken to the basis $\{f_{\ell,k}\}$ on the right.
%\end{remark}
\begin{corollary}
  \label{cor:preprojective homomorphism duality}
  The sequence \eqref{eq:AR sequence} gives rise to an isomorphism $H_m^*\cong H_{m-1}$.
\end{corollary}
\begin{proof}
  Define a map $\Theta:H_m^*\to H_{m-1}$ by $\Theta(\varphi)=(id\overline{\otimes}\varphi)\circ\iota_{m-1}$, in words $\Theta(\varphi)$ acts on $x\in P_{m-1}$ by contracting with the second factor in $\iota_{m-1}(x)$ to give an element of $P_m$.
  Suppose $\varphi\in H_m^*$ is a nonzero functional on $H_m$ and let $V\subsetneq H_m$ denote the kernel of $\varphi$.
  Then $\Theta(\varphi)=0\in H_{m-1}$ if and only if the image of $\iota_{m-1}$ is contained in $P_m\otimes V\subsetneq P_m\otimes H_m$.
  But then Lemma~\ref{le:injective evaluation maps} implies $\iota_{m-1}$ is the zero map, a contradiction.
  Thus $\Theta:H_m^*\to H_{m-1}$ must be injective and hence an isomorphism.
\end{proof}
\begin{remark}
  The set $Gr(H_m)$ is naturally a poset and Corollary~\ref{cor:preprojective homomorphism duality} gives an identification of the opposite poset $Gr(H_m)^{op}\cong Gr(H_m^*)$ with $Gr(H_{m-1})$.
  We write $\bar{V}\subset H_{m-1}$ for the subspace corresponding to $V\subset H_m$ under this identification.
  Under the isomorphism of $H_{m-1}$ with $H_m^*$, we have $\bar{V}=(H_m/V)^*$.
\end{remark}

\begin{definition}
  For $V\in Gr(H_m)$, define the \emph{truncated preprojective} $P_{m+1}^V$ to be the cokernel of the map $ev_V:P_m\otimes V\to P_{m+1}$, i.e.\ we have a short exact sequence
  \begin{equation}
    \label{eq:truncated preprojectives}
    0\longrightarrow P_m\otimes V\stackrel{ev_V}{\longrightarrow} P_{m+1}\stackrel{\pi_V}{\longrightarrow} P_{m+1}^V\longrightarrow 0.
  \end{equation}
\end{definition}
\begin{remark}
  It will be convenient to also set $P_{m+1}^0=P_{m+1}$, observe that this notation is consistent with taking $V=0$ in the sequence \eqref{eq:truncated preprojectives}.
\end{remark}

\begin{lemma}
  \label{le:basic homological properties}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_{m+1}^V,P_\ell)=0=\Ext(P_\ell,P_{m+1}^V)$ for all $\ell\ge1$.
  Moreover, $\Hom(P_{m+1},P_{m+1}^V)$ is the one-dimensional space spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{lemma}
\begin{proof}
  The first claim is immediate since $\Hom(X,P_\ell)\ne0$ (resp. $\Ext(P_\ell,X)\ne0$) for some $\ell\ge1$ implies all indecomposable summands of $X$ are preprojectives of the form $P_r$ with $1\le r\le\ell$ (resp. $1\le r\le\ell-2$), whereas $P_{m+1}^V$ is not preprojective.
  For the second claim we apply the functor $\Hom(P_{m+1},-)$ to the sequence \eqref{eq:truncated preprojectives} and obtain an isomorphism $\Hom(P_{m+1},P_{m+1})\cong\Hom(P_{m+1},P_{m+1}^V)$ by which the identity map on $P_{m+1}$ is taken to the projection $\pi_V:P_{m+1}\to P_{m+1}^V$.
\end{proof}

\begin{corollary}
  For $V\in Gr(H_m)$, $m\ge1$, the truncated preprojective $P_{m+1}^V$ is indecomposable.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map from $\Hom(P_{m+1}^V,P_{m+1}^V)$ to the one-dimensional space $\Hom(P_{m+1},P_{m+1}^V)$.
  In particular, the endomorphism ring of $P_{m+1}^V$ is one-dimensional and so $P_{m+1}^V$ must be indecomposable.
\end{proof}

The total Grassmannian $Gr(H_m)$ is naturally a poset under inclusion which we extend to a $\CC$-linear category $\CC Gr(H_m)$ with objects the elements of $Gr(H_m)$ and at most one morphism (up to scalars) between any two objects.
Write $\cP_{m+1}$ for the full subcategory of $\rep K(n)$ with objects the truncated preprojectives $P_{m+1}^V$ for $V\in Gr(H_m)$.
\begin{lemma}
  \label{le:unique morphisms}
  The functor $V\mapsto P_{m+1}^V$ gives an isomorphism of categories $\CC Gr(H_m)\cong\cP_{m+1}$.
  In particular, there exists a morphism $P_{m+1}^W\to P_{m+1}^V$ for $V,W\in Gr(H_m)$ if and only if $W\subset V$ and this morphism is unique (up to scalars) when it exists.
\end{lemma}
\begin{proof}
  Given $V,W\in Gr(H_m)$, we apply the functor $\Hom(-,P_{m+1}^V)$ to the sequence \eqref{eq:truncated preprojectives} for $W$ to get an exact sequence
  \[0\longrightarrow \Hom(P_{m+1}^W,P_{m+1}^V)\longrightarrow \Hom(P_{m+1},P_{m+1}^V)\stackrel{-\circ ev_W}{\longrightarrow} \Hom(P_m\otimes W,P_{m+1}^V).\]
  But the space $\Hom(P_{m+1},P_{m+1}^V)$ is one-dimensional, spanned by the natural projection $\pi_V:P_{m+1}\to P_{m+1}^V$, and thus $\Hom(P_{m+1}^W,P_{m+1}^V)$ is nonzero if and only if the right hand morphism of the above sequence is zero.
  But this occurs exactly when the image of $ev_W:P_m\otimes W\to P_{m+1}$ is contained in the kernel of $\pi_V$, i.e.\ in the image of $ev_V:P_m\otimes V\to P_{m+1}$, and this occurs if and only if $W\subset V$. 
\end{proof}

\begin{lemma}
  \label{le:irreducible morphisms}
  For $V\in Gr(H_m)$, $m\ge1$, and $W\subsetneq V$ with $\codim_V W=1$, the unique morphism $P_{m+1}^W\to P_{m+1}^V$ is irreducible.
\end{lemma}
In particular, the poset $Gr(H_m)$, thought of as a directed graph, can be identified with a subset of the Auslander-Reiten quiver of $K(n)$.

\begin{lemma}
  \label{le:truncated homomorphisms}
  For $V\in Gr(H_m)$, $m\ge1$, we have $\Hom(P_m,P_{m+1}^V)\cong H_m/V$.
\end{lemma}
\begin{proof}
  Applying the functor $\Hom(P_m,-)$ to the sequence \eqref{eq:truncated preprojectives} gives an exact sequence
  \[\xymatrix{0 \ar[r] & \Hom(P_m,P_m\otimes V) \ar[r] & \Hom(P_m,P_{m+1}) \ar[r] & \Hom(P_m,P_{m+1}^V) \ar[r] & 0}.\]
  But there is a natural isomorphism $\Hom(P_m,P_m\otimes V)\cong V$ and the result follows.
\end{proof}

\begin{corollary}
    For $V,W\in Gr(H_m)$ with $V\subset W$, we have $\Ext(P_{m+1}^V,P_{m+1}^W)\cong V^*\otimes(H_m/W)$.
\end{corollary}
\begin{proof}
  Applying the functor $\Hom(-,P_{m+1}^W)$ to the sequence \eqref{eq:truncated preprojectives} gives an injective map $\Hom(P_{m+1}^V,P_{m+1}^W)\to\Hom(P_{m+1},P_{m+1}^W)$ which is an isomorphism by Lemma~\ref{le:basic homological properties} and Lemma~\ref{le:unique morphisms}.
  Since $\Ext(P_{m+1},P_{m+1}^W)=0$ again by Lemma~\ref{le:basic homological properties}, it follows that there is an isomorphism 
  \[\Ext(P_{m+1}^V,P_{m+1}^W)\cong\Hom(P_m\otimes V,P_{m+1}^W)\cong V^*\otimes H_m/W,\]
  where the last isomorphism is immediate from Lemma~\ref{le:truncated homomorphisms}.
\end{proof}
